Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-05-28 Text/Reviews/ResponsesR0R1-Reviewer1.tex

\vspace{3em}
\begin{reviewbox}{Comment 5}
Page 16, line 269. Could you comment on why you selected a 7x7 window?
\end{reviewbox}
\begin{responsebox}{Response}

In SAR image processing, the selection of window size is crucial. Very large windows can average out local details, reducing sensitivity to fine-scale variations, while very small windows may not provide enough data for reliable statistical estimates. Our choice of a $7\times 7$ window strikes a balance, capturing detailed local information while ensuring sufficient data points for robust analysis. Additionally, practical scenarios in SAR image processing often involve small sample sizes, typically obtained over windows of size $7\times 7$.

We have clarified (line 280) that
\begin{quote}
	\textcolor{blue}{The three statistical tests are applied to the SAR images using $7\times 7$ local sliding windows.
		This window size balances detailed local information and sufficient number of data points, as illustrated in Figures [\dots]}
\end{quote}
\end{responsebox}

\vspace{3em}
\begin{reviewbox}{Comment 6}
As a suggestion, in order to conduct a more quantitative analysis of the results for each estimator, would you consider comparing the mean and standard deviation values of the different tests among some reference areas in the images? Ideally, a land cover map would serve. Alternatively, you may use some polygons with a clear land cover label (water, vegetation, urban). This would also serve to evaluate the sensitivity of the estimators for classification purposes.
\end{reviewbox}
\begin{responsebox}{Response}
We conducted a quantitative analysis by comparing the mean values and standard deviations of the different tests in selected reference areas in the image, as recommended.

 We added a new section in the results (line 314). The results presented in Table 10 show that the estimators are sensitive to differences in land cover, which is essential for classification purposes. Homogeneous (water) areas have lower mean and standard deviation values, while heterogeneous (urban) areas have the highest values.

\end{responsebox}

### 2024-05-28 Text/R1-Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
add quantitative analysis line 314

>>>>

## Quantitative Analysis of Test Statistics
In order to conduct a more quantitative analysis of the results, we compared the mean and standard deviation values of the different tests among selected reference areas in the Illinois-Region 2 image. These reference areas represent water, vegetation, and urban land covers, as shown in Figure&nbsp;\ref{fig:land_cover}.

We selected labeled polygons (water, vegetation, urban) and conducted 100 sampling iterations with replacement from each category, using window sizes of $11\times11$ pixels. For each sample, we applied the corresponding test statistic. Finally, we computed the mean and standard deviation of the results obtained from the 100 samples.

\renewcommand{\arraystretch}{1}  
```{r land_cover, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="50%", fig.align="center",fig.pos = 'H', fig.cap='Image of Illinois-Region 2 with reference samples. ',   fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/land_cover.pdf")
```

The Table&nbsp;\ref{tab:table_M_sd} presents the comparison of the mean and standard deviation values for the three  tests across the reference areas.
```{r parameters_land, echo=FALSE, message=FALSE, warning=FALSE}

#
results_comparison_data <- data.frame(
  Area_of_Reference = c("Water", "Water", "Water", "Vegetation", "Vegetation", "Vegetation", "Urban", "Urban", "Urban"),
  Statistical_Test = rep(c("$S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$", "$T_\\text{CV}$", "$T_{\\text{CV}_{\\text{MnAD}}}$"), 3),
  Mean = c("0.05029", "0.15827", "0.13013", "0.36482", "0.29421", "0.24501", "0.82970", "0.56846", "0.47176"),
  Standard_Deviation = c("0.15415", "0.02584", "0.02183", "0.28489", "0.10957", "0.09829", "0.21910", "0.33938", "0.29486")
)

colnames(results_comparison_data) <- c("\\textbf{Area of Reference}", "\\textbf{Test Statistic}", "\\textbf{Mean}", "\\textbf{SD}")
results_comparison_data[] <- lapply(results_comparison_data, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.5f$", x), sprintf("$\\phantom{-}%.5f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

kable(results_comparison_data, caption = "Analysis of  test statistics for different areas of reference.",
      format = "latex",
      booktabs = TRUE,
      align = "ccccccccc",
      escape = FALSE,
      digits = 5,
      label = "table_M_sd",
      centering = FALSE,
      table.envir = "table", position = "H") %>%
  row_spec(0, align = "c") %>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  kable_styling(latex_options = "scale_down", font_size = 9) %>% 
  kable_styling(full_width = TRUE) %>%
  column_spec(1, width = "3.5cm") %>%
  column_spec(2, width = "5cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm")

Based on the analysis, $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ appears to be the most sensitive test for classification purposes because it shows the largest distinction in mean values between the different land cover types, indicating it is better at differentiating between homogeneous and heterogeneous areas. However, CV and $\text{CV}_{\text{MnAD}}$ are also reliable with lower variability, making them good candidates depending on the specific application.
